Differentiable Optics with dLux: I - Deep Calibration of Flat Field and Phase with Automatic Differentiation

### 2022-11-10 src/tex/ms.tex
[showyourwork] overleaf sync

\affil[a]{Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW~2006, Australia}
\affil[b]{School of Mathematics and Physics, University of Queensland, St Lucia, QLD~4072, Australia}
\affil[c]{Centre for Astrophysics, University of Southern Queensland, West Street, Toowoomba, QLD~4350, Australia}

>>>>

% \affil[a]{Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW~2006, Australia}
% \affil[b]{School of Mathematics and Physics, University of Queensland, St Lucia, QLD~4072, Australia}
% \affil[c]{Centre for Astrophysics, University of Southern Queensland, West Street, Toowoomba, QLD~4350, Australia}
